\GVN{}-Hoist: Hoisting Computations from Branches

### 2016-08-25 hoist.tex
add discussion about GEP hoisting at -Oz

>>>>

In order to reduce register pressure, we have restricted hoisting of address
computations away from their corresponding loads and stores when the loads and
stores cannot be moved.  This restriction is lifted when aggressively optimizing
for size (in -Oz).  We have seen several uplifts and degradations in performance
of the generated code on several benchmarks, and to avoid the degradations we
decided to only enable hoisting of getElementPtrs without their associated
memory operations when optimizing for size.  This restriction may be lifted in
the future, either when the register allocation rematerialization pass has been
improved to catch the regressions, or by implementing more precise heuristics
for code hoisting.
